Integer Programming Formulations for the Shared Multicast Tree Problem

### 2018-09-26 smt/response.tex

\documentclass[12pt]{article}
\usepackage{a4wide,url}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{color}

\begin{document}
\section*{Response Letter}
We are grateful to the reviewers for their time, effort, and constructive remarks.
All remarks have been accounted for in the revised version, as detailed in our response below.

\section*{Reviewer 2}
Our response in \textcolor{blue}{blue} follows the corresponding remark from the reviewer in \textcolor{red}{red}.

\begin{itemize}
\item \textcolor{red}{The abstract should be shorter.} \textcolor{blue}{
We have revised the abstract, and reduced its length from 22 to 15 lines.
}
\item \textcolor{red}{The literature review has not been organized in a proper format. The references are so old. New related works need to be explained. The authors should use a separate Section for this purpose and compare the novelty of the present approach with them.} \textcolor{blue}{
Following the recommendation of the reviewer, we have reorganized the literature review, and devoted a new section (Section 2 in the revised manuscript)
to this topic. We have also included a review of more recent and relevant literature (references \cite{bein10, bhukya14}).
In Section 1.2, we now state explicitly the contributions from the present work, and explain how they relate to the current literature.
}
\item \textcolor{red}{They also should consider a separate section on the network model and assumptions.} \textcolor{blue}{
We have restructured the former Section 2 (now Section 3) into three subsections.
The first is devoted to mathematical notation and underlying assumptions, the second addresses the network model,
while the problem definition is given in the third subsection.
}
\item \textcolor{red}{The diagrams of figures are not distinguishable in black and white print. The legends should be corrected.} \textcolor{blue}{
While paying particular attention to their appearance in black and white print, we have given all figures,
including their legends, a complete overhaul.
}
\item \textcolor{red}{All equations should be terminated with "." or "," as well as sentences.} \textcolor{blue}{
Done.
}
\item \textcolor{red}{The legends, markers and other details of the figures are so small.} \textcolor{blue}{
Legends, markers, and other details are now given in larger size.
}
\item \textcolor{red}{A fundamental weak point is that there are no numerical results comparing the proposed scheme with the other new works;} \textcolor{blue}{
We agree that a comparison with alternative contemporary methods largely benefits the paper.
To that end, we have included a comparison with a recently published metaheuristic algorithm, based on iterative combination of elite solutions \cite{pajor18}.
The method is described in the new Section 7, and results from experiments with the method are presented in the new Section 8.3.
}
\item \textcolor{red}{The simulation graphs need more expiation and justification.} \textcolor{blue}{
For better justification of the numerical results illustrated graphically in the former Section 6 (now Section 8),
we have added more explanations both in the caption of Fig.\ 3 and in the text referring to the figure.
}
\item \textcolor{red}{ The main aim of this paper is the energy, How is the energy issue modeled? Why is not the real models used in the paper?} \textcolor{blue}{
In the new Section 3.2 on the network model, we now explain more detailed how the energy is modeled.
At the end of the section, we also describe how our energy model relates to others in the literature.
Justification is added in terms of references to \cite{halgamuge}, and to other relevant and frequently cited works mentioned in Section 2 (Wieselthier et al. (2000), Das et al. (2003), Altinkemer et al. (2005),
Yuan (2005), Yuan et al. (2008), Bauer et al. (2008), Montemanni and Leggieri (2011) and Leggieri et al. (2008), etc.).
See also our response to the second remark of Reviewer 3.
}
\item \textcolor{red}{Overall the novelty of the proposed approach in unclear and the paper is hard to follow
The authors have not considers the wireless problems in the paper.} \textcolor{blue}{
The novelty of and the contributions from the paper are now explicitly stated in Section 2.
We also explain how the paper relates to other works on energy minimization in wireless networks.
}
\end{itemize}

### 2018-09-26 smt/ivanova.tex
DH: Added a section on the heuristic in a separate file. File names should be updated to become consistent with section numbers.
MI (SMT): Minor changes in several files, mainly in Sect 8 - description of the results.
DH: Minor revision of the bibliography and the response letter.

\input{sec1-intro.tex}
\input{sec2-literature.tex}
\input{sec2-sbtsmt.tex}
\input{sec3-milp.tex}
\input{sec4-relations.tex}
\input{sec5-strong.tex}
\input{sec6-exp.tex}
\input{sec7-conclusion.tex}

@@

\bibitem[Guo and Yang(2004)]{guo}
Guo S, Yang O (2004)
Minimum Energy Multicast Routing for Wireless Ad-hoc Networks with Adaptive Antennas 
In: Proceedings of the 12th IEEE International Conference on Network Protocols ICNP 2004,
pp 151--160

>>>>

\input{sec1-intro.tex}
\input{sec2-literature.tex}
\input{sec3-sbtsmt.tex}
\input{sec4-milp.tex}
\input{sec5-relations.tex}
\input{sec6-strong.tex}
\input{sec7-heur.tex}
\input{sec8-exp.tex}
\input{sec9-conclusion.tex}

@@

\bibitem[Guo and Yang(2004)]{guo}
\textcolor{blue}{Guo S, Yang O (2004)
Minimum Energy Multicast Routing for Wireless Ad-hoc Networks with Adaptive Antennas 
In: Proceedings of the 12th IEEE International Conference on Network Protocols ICNP 2004,
pp 151--160}
